Stagnating State Funding for Higher Education and its Effect on Faculty at US Universities

### 2023-08-17 text/sections/09-figures-tables.tex
adjusted writing.

    \justify
    \footnotesize
    \textbf{Note}:
    These tables show the OLS estimates of regression specification \eqref{eqn:firststage}, showing the effect of the funding shock on other outcomes to gauge balance of the instrument with respect to university characteristics
    Enrolment is measured in thousands of students.
    Each observation is a public univeristy-year, in the IPEDS data.
    Panel A shows the effect of an funding shock of \$$-1,000$ per student in the state on the counts of the outcome --- i.e.,
    \$$-1,000$ funding shock per student in the state is associated with 517 more students (as enrolment is measured in thousands) in column 1.
    Panel B shows the effect of a $-10$\% change funding shock per student in the state on $10$\% change in the outcomes --- i.e.,
    $-10$\% funding shock per student in the state is associated with an increase in 1.07\% more students at the unviersity according to prefferred column 1.        
    Standard errors are clustered at the state-year level, and univeristy $+$ year fixed effects are included where noted.
    \label{tab:firststage-balance}
\end{table}

>>>>

    \justify
    \footnotesize
    \textbf{Note}:
    These tables show the OLS estimates of regression specification \eqref{eqn:firststage}, showing the effect of the funding shock on other outcomes to gauge balance of the instrument with respect to university characteristics
    Enrolment is measured in thousands of students.
    Each observation is a public universit--year, in the IPEDS data.
    Panel A shows the effect of a funding shock of \$$-1,000$ (per student in the state) on the outcome --- i.e.,
    \$$-1,000$ funding shock per student in the state is associated with 517 more students (as enrolment is measured in thousands) in column 1.
    Panel B shows the effect of a $-10$\% change funding shock per student in the state on $10$\% change in the outcomes --- i.e.,
    $-10$\% funding shock per student in the state is associated with an increase in 1.07\% more students at the university according to preferred column 1.
    Standard errors are clustered at the state-year level, and university $+$ year fixed effects are included where noted.
    \label{tab:firststage-balance}
\end{table}
